|

### 2019-09-03 article/article.Rmd
Changes Mignozzetti

---
title:  |
        | Bottom-Up Accountability and Public Service Provision: Evidence from a Field Experiment in Brazil
author: 
- "Danilo Freire[^freire]"
- "Manoel Galdino[^galdino]"
- "Umberto Mignozzetti[^mignozzetti]"
date: \today
thanks: "We thank Fábio Barros, Guilherme Jardim Duarte, Stephen Herzog and David Skarbek for their helpful comments. We are specially grateful to Catarina Roman and the staff of Transparência Brasil for their excellent research assistance. This research was pre-registered on the EGAP pre-registry tool (<https://egap.org/registration/4505>) and approved by the Brazilian Ministry of Education. The authors thank the 2016 Google Social Impact Challenge for financial support and declare there are no conflict of interest. Replication data and code are available at <http://github.com/umbertomignozzetti/tdp-accountability>."
abstract: "Does grassroots participation improve public service delivery? We study the effect of a mobile phone application that allows citizens to monitor school construction projects in 1020 Brazilian municipalities. The app provides a platform where users can submit photos of construction sites, consult independent engineers, and contact the mayor's office about project delays. Our results show that the app has a null impact on the school construction outcomes. Additionally, we find that politicians are unresponsive to individual requests. The results question the impact of local monitoring on public service performance and suggest that interventions targeted at other groups may produce better policy outcomes."
abstractspacing: double
keywords: accountability, Brazil, impact evaluation, state capacity, technology
fontsize: 12pt
margin: 
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    template: article-template.latex
---

@@

## Analysis Intervention 1

## Covariate balance
aux <- select(impEvalph1, 
              treatOriginal, logPop2015,
              ideb_ai_2015, ideb_af_2015, log_poorFam2010,
              log_totTransf2016) %>%
  unique()
resu1 <- compareGroups(treatOriginal ~ 
                         logPop2015 + 
                         log_poorFam2010 +
                         log_totTransf2016 +
                         ideb_ai_2015 + 
                         ideb_af_2015, 
                       data = aux)
tabIE1balance <- createTable(resu1, digits = 3)
row.names(tabIE1balance$descr) <- 
  c('Log Population (2015)', 
    'Log Poor Families (2010)', 
    'Log Total Transfers (2016)', 
    'IDEB Inicial Years (2015)', 
    'IDEB Final Years (2015)')

## Map GA intervention 1
mapbr <- get_brmap('City')
gaaux <- filter(ga, phase1 == 1)
gaaux <- select(gaaux, ibge_code7, downl)
gaaux <- rename(gaaux, City = ibge_code7)
gaaux <- unique(gaaux)
gaaux$City <- as.numeric(gaaux$City)
gaaux2 <- impEvalph2 %>%
  select(ibge_code7) %>%
  transmute(City = as.numeric(ibge_code7)) %>%
  unique()
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 0
gaaux2 <- data.frame(City = mapbr$City)
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 2
gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads', 'Not in App'))
mapbr <- join_data(mapbr, gaaux, by = 'City')
pMapDownloadsInt1 <- ggplot() + 
  geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.02) +
  scale_fill_manual(values=c( "#E69F00", "#0072B2", "#F0E442")) +
  theme_map()
pMapDownloadsInt1

@@

## Map intervention 2
mapbr <- get_brmap('City')
gaaux <- filter(ga, phase2 == 1)
gaaux <- select(gaaux, ibge_code7, downl)
gaaux <- rename(gaaux, City = ibge_code7)
gaaux <- unique(gaaux)
gaaux$City <- as.numeric(gaaux$City)
gaaux2 <- impEvalph2 %>%
  select(ibge_code7) %>%
  transmute(City = as.numeric(ibge_code7)) %>%
  unique()
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 0
gaaux2 <- data.frame(City = mapbr$City)
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 2
gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads', 'Not in App'))
mapbr <- join_data(mapbr, gaaux, by = 'City')
p1 <- ggplot() + 
  geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.02) +
  scale_fill_manual(values=c( "#E69F00", "#0072B2", "#F0E442")) +
  theme_map()
p1

@@

resInt1 <- calcATEs(outcs, treats, ctrls, fes, cls, dat = impEvalph1)

@@

\begin{table}[!htbp] \centering 
  \caption{\label{tab:results1} Impact Evaluation -- Intervention 1} 
  \label{} 
\begin{tabular}{@{\extracolsep{-2pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
\cline{2-7} 
 & Investment & Investment & Delta & Finished & Cancelled & Updated \\ & Before & After & Investment & Construction & Construction & Date \\ &  &  &  &  &  \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
\hline \\[-1.8ex] 
 ATE & 1.26 & 1.83 & 0.57 & 0.05$^{***}$ & 0.03$^{***}$ & 0.06 \\ 
  & (2.69) & (3.06) & (0.93) & (0.01) & (0.01) & (0.04) \\ 
  & & & & & & \\ 
\hline \\[-1.8ex] 
Controls & Yes & Yes & Yes & Yes & Yes & Yes \\ 
State fixed effects & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 3,602 & 3,602 & 3,602 & 3,602 & 3,602 & 2,352 \\ 
R$^{2}$ & 0.13 & 0.13 & 0.05 & 0.03 & 0.05 & 0.08 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{6}{r}{Cluster-robust SEs at the municipality level.} \\ 
\end{tabular} 
\end{table}

We find that the intervention is sufficient to improve school completion and cancellation rates. The TDP application increases in `r round(100*resInt1[[2]][[16]]$coefficients[1], 0)` percent the chance that a school construction is reported as finished by the end of the intervention. The treatment also increases the likelihood of cancelling the construction in `r round(100*resInt1[[2]][[20]]$coefficients[1], 0)` percent. While the first result is in line with our theoretical expectations, the second one goes in the opposite direction. But as we discuss below, the findings are inconsistent and do not replicate in the second experiment. All other coefficients are not statistically significant at conventional levels. On the one hand, the results indicate that our placebo outcome, the percentage of the invested executed before the intervention, indeed behaves as predicted. On the other hand, we expected the four remaining outcomes to improve after the introduction of the app. The literature on bottom-up accountability argues that more information about the shortcomings of public service provision will mobilise citizens who, in turn, would pressure state agents to produce better social policies. Our results do not lend support to that hypothesis.

@@

@@

resInt2 <- calcATEs(outcs, 'treatApp', ctrls, fes, cls, dat = impEvalph2)

# Results intervention 2
library(stargazer)
stargazer(resInt2[[2]][[4]],resInt2[[2]][[8]],resInt2[[2]][[12]],
          resInt2[[2]][[16]],resInt2[[2]][[20]],resInt2[[2]][[24]],
          title = '\\label{tab:results2} Impact Evaluation -- Intervention 2',
          dep.var.labels.include=F, 
          keep='treatAppTreatment', type = 'latex',
          covariate.labels = 'ATE',
          column.labels = c("Investment & Investment & Delta & Finished & Cancelled & Updated \\\\ & Before & After & Investment & Construction & Construction & Date \\\\"),
          column.sep.width = '-2pt',
          omit.stat=c('adj.rsq', 'ser'), align=F, digits=2,
          notes = 'Cluster-robust SEs at the municipality level.',
          add.lines = list(c("Controls", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
            c("State Fixed Effects", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes")),
          notes.append = T, header=FALSE)
```

@@

\begin{table}[!htbp] \centering 
  \caption{\label{tab:results2} Impact Evaluation -- Intervention 2} 
  \label{} 
\begin{tabular}{@{\extracolsep{-2pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
\cline{2-7} 
 & Investment & Investment & Delta & Finished & Cancelled & Updated \\ & Before & After & Investment & Construction & Construction & Date \\ &  &  &  &  &  \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
\hline \\[-1.8ex] 
 ATE & $-$1.16 & $-$1.01 & 0.14 & $-$0.002 & $-$0.0001 & 0.00 \\ 
  & (1.40) & (1.50) & (0.54) & (0.01) & (0.01) & (0.00) \\ 
  & & & & & & \\ 
\hline \\[-1.8ex] 
Controls & Yes & Yes & Yes & Yes & Yes & Yes \\ 
State Fixed Effects & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 3,364 & 3,364 & 3,364 & 3,364 & 3,364 & 2,304 \\ 
R$^{2}$ & 0.10 & 0.10 & 0.03 & 0.02 & 0.18 &  \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{6}{r}{Cluster-robust SEs at the municipality level.} \\ 
\end{tabular} 
\end{table}

@@

# Function for custom randomization inference
test_fun <- function(dat, outc, treat, wts = NULL) {
  ctrls_mod <- paste(ctrls, collapse = '+')
  fes_mod <- paste(fes, collapse = '+')
  moddescr <- data.frame()
  mods <- list()
  if(is.null(wts)) {
    dat <- dat %>%
      select(one_of(c(outc, treat, ctrls, fes, cls))) %>%
      na.omit()
  } else {
    dat <- dat %>%
      select(one_of(c(outc, treat, ctrls, fes, cls, wts))) %>%
      na.omit()
    wts <- dat[,wts]
  }
  aux <- 
    felm(as.formula(
      paste(c(outc,paste(paste(c(treat,ctrls_mod), collapse = '+'),
                        paste('',fes_mod,0,cls, sep = '|'), sep = '')),
              collapse = '~')), data = dat, weights = wts)
  return(aux$coefficients[1])
}

@@

# First experiment
set.seed(543129) #Random.org
auxdat <- impEvalph1[,c('ibge_code7', outcs, ctrls, fes, cls)]
aux2 <- unique(impEvalph1[,c('ibge_code7', 'treat')]) %>% na.omit()
N = sum(table(aux2$treat))
Ctrl = 150
resri1 <- data.frame(1:1000)
for (k in 1:1000) {
    treat <- c(rep(1,N-Ctrl), rep(0,Ctrl))
    treat <- sample(treat, N)
    aux2 <- data.frame(aux2, treat = treat)
}
auxdat <- left_join(auxdat, aux2)
for (i in outcs) {
  res <- numeric()
  for (k in 1:1000) 
    res[k] <- test_fun(auxdat, i, paste('treat', k, sep = '.'))
  resri1 <- data.frame(resri1, res)
  names(resri1)[names(resri1)=='res'] = i
}
resri1 <- resri1[,-1]
i1h1 <- ggplot(data=resri1, aes(resri1$percExecBegin)) + 
  geom_histogram(bins = 100) + 
  geom_vline(xintercept = test_fun(impEvalph1, 'percExecBegin', 'treat'),
             lwd = 1, lty = 2) +
  labs(x="Percentage Completed Before\n(placebo)", y="Frequency")
i1h2 <- ggplot(data=resri1, aes(resri1$percExecEnd)) + 
  geom_histogram(bins = 100) + 
  geom_vline(xintercept = test_fun(impEvalph1, 'percExecEnd', 'treat'),
             lwd = 1, lty = 2) +
  labs(x="Percentage Completed End Intervention", y="Frequency")
i1h3 <- ggplot(data=resri1, aes(resri1$deltaPercExec)) + 
  geom_histogram(bins = 100) + 
  geom_vline(xintercept = test_fun(impEvalph1, 'deltaPercExec', 'treat'),
             lwd = 1, lty = 2) +
  labs(x="Diff. Pct. Completed Before and After", y="Frequency")
i1h4 <- ggplot(data=resri1, aes(resri1$isFinished)) + 
  geom_histogram(bins = 100) + 
  geom_vline(xintercept = test_fun(impEvalph1, 'isFinished', 'treat'),
             lwd = 1, lty = 2) +
  labs(x="Finished School Construction Indicator", y="Frequency")
i1h5 <- ggplot(data=resri1, aes(resri1$isCancelled)) + 
  geom_histogram(bins = 100) + 
  geom_vline(xintercept = test_fun(impEvalph1, 'isCancelled', 'treat'),
             lwd = 1, lty = 2) +
  labs(x="Cancelled School Construction Indicator", y="Frequency")
i1h6 <- ggplot(data=resri1, aes(resri1$updDate)) + 
  geom_histogram(bins = 100) + 
  geom_vline(xintercept = test_fun(impEvalph1, 'updDate', 'treat'),
             lwd = 1, lty = 2) +
  labs(x="Updated Endline Date School Construction", y="Frequency")

@@

We also note that effect sizes are small in all estimations and coefficients flip signs in all but one of our six dependent variables. This provides further evidence for the null results: not only the app would have a low impact even if the treatment were significant, but the results could go against what the bottom-up accountability theory predicts. At least in the school construction outcomes we investigate here, we find little evidence that grassroots monitoring works.

>>>>

---
title:  |
        | Bottom-Up Accountability and Public Service Provision: Evidence from a Field Experiment in Brazil
author: 
- "Danilo Freire[^freire]"
- "Manoel Galdino[^galdino]"
- "Umberto Mignozzetti[^mignozzetti]"
date: \today
thanks: "We thank Fábio Barros, Guilherme Jardim Duarte, Stephen Herzog and David Skarbek for their helpful comments. We are specially grateful to Catarina Roman and the staff of Transparência Brasil for their excellent research assistance. This research was pre-registered on the EGAP pre-registry tool (<https://egap.org/registration/4505>) and approved by the Brazilian Ministry of Education. The authors thank the 2016 Google Social Impact Challenge for financial support and declare there are no conflict of interest. Replication data and code are available at <http://github.com/umbertomignozzetti/tdp-accountability>."
abstract: "Does grassroots participation improve public service delivery? We study the effect of a mobile phone application that allows citizens to monitor school construction projects in Brazilian municipalities. The app provides a platform where users can submit photos of construction sites, consult independent engineers, and contact the mayor's office about project delays. Our results show that the app has a null impact on the school construction outcomes. Additionally, we find that politicians are unresponsive to individual requests. The results question the impact of local monitoring on public service performance and suggest that interventions targeted at other groups may produce better policy outcomes."
abstractspacing: double
keywords: accountability, Brazil, impact evaluation, state capacity, technology
fontsize: 12pt
margin: 
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    template: article-template.latex
---

@@

## Map GA intervention 1
mapbr <- get_brmap('City')
gaaux <- filter(ga, phase1 == 1)
gaaux <- select(gaaux, ibge_code7, downl)
gaaux <- rename(gaaux, City = ibge_code7)
gaaux <- unique(gaaux)
gaaux$City <- as.numeric(gaaux$City)
gaaux2 <- impact_evaluation_phase2 %>%
  select(ibge_code7) %>%
  transmute(City = as.numeric(ibge_code7)) %>%
  unique()
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 0
gaaux2 <- data.frame(City = mapbr$City)
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 2
gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads', 'Not in App'))
mapbr <- join_data(mapbr, gaaux, by = 'City')
pMapDownloadsInt1 <- ggplot() + 
  geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.02) +
  scale_fill_manual(values=c( "#E69F00", "#0072B2", "#F0E442")) +
  theme_map()
pMapDownloadsInt1

@@

## Map intervention 2
mapbr <- get_brmap('City')
gaaux <- filter(ga, phase2 == 1)
gaaux <- select(gaaux, ibge_code7, downl)
gaaux <- rename(gaaux, City = ibge_code7)
gaaux <- unique(gaaux)
gaaux$City <- as.numeric(gaaux$City)
gaaux2 <- impact_evaluation_phase2 %>%
  select(ibge_code7) %>%
  transmute(City = as.numeric(ibge_code7)) %>%
  unique()
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 0
gaaux2 <- data.frame(City = mapbr$City)
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 2
gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads', 'Not in App'))
mapbr <- join_data(mapbr, gaaux, by = 'City')
p1 <- ggplot() + 
  geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.02) +
  scale_fill_manual(values=c( "#E69F00", "#0072B2", "#F0E442")) +
  theme_map()
p1

@@

resInt1 <- calcATEs(outcs, treats, ctrls, fes, cls, dat = impact_evaluation_phase1)

@@

\begin{table}[!htbp] \centering 
  \caption{\label{tab:results1} Impact Evaluation -- Intervention 1} 
  \label{} 
\begin{tabular}{@{\extracolsep{-2pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
\cline{2-7} 
 & Investment & Investment & Delta & Finished & Cancelled & Updated \\ & Before & After & Investment & Construction & Construction & Date \\ &  &  &  &  &  \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
\hline \\[-1.8ex] 
 ATE & $-$0.99 & $-$1.12 & $-$0.13 & 0.002 & 0.02$^{**}$ & 0.05 \\ 
  & (2.59) & (2.96) & (1.03) & (0.01) & (0.01) & (0.05) \\ 
  & & & & & & \\ 
\hline \\[-1.8ex] 
Controls & Yes & Yes & Yes & Yes & Yes & Yes \\ 
State fixed effects & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 2,986 & 2,986 & 2,986 & 2,986 & 2,986 & 2,926 \\ 
R$^{2}$ & 0.16 & 0.14 & 0.05 & 0.02 & 0.07 & 0.13 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{6}{r}{Cluster-robust SEs at the municipality level.} \\ 
\end{tabular} 
\end{table}

We find that only has a small effect on cancellation rates. The TDP application increases the likelihood of cancelling the construction in `r round(100*resInt1[[2]][[20]]$coefficients[1], 2)` percent. While this result goes in the opposite direction of our theoretical expectations, the finding is largely inconsistent, and do not replicate in the second experiment. All other coefficients are not statistically significant at conventional levels. On the one hand, the results indicate that our placebo outcome, the percentage of the invested executed before the intervention, indeed behaves as predicted. On the other hand, we expected the five remaining outcomes to improve after the introduction of the app. The literature on bottom-up accountability argues that more information about the shortcomings of public service provision will mobilise citizens who, in turn, would pressure state agents to produce better social policies. Our results do not lend support to that hypothesis.

@@

# Auxiliary function: calculate coefficients
calcATEs <- function(outcs, treats, ctrls, fes, cls, dat, wts = NULL, ...) {
  ctrls_mod <- paste(ctrls, collapse = '+')
  fes_mod <- paste(fes, collapse = '+')
  moddescr <- data.frame()
  mods <- list()
  dataux <- dat
  k <- 1
  for (i in treats) {
    for (j in outcs) {
      if(is.null(wts)) {
        dat <- dataux %>%
          select(one_of(c(j, treats, ctrls, fes, cls))) %>%
          na.omit()
        wtsaux <- NULL
      } else {
          dat <- dataux %>%
            select(one_of(c(j, treats, ctrls, fes, cls, wts))) %>%
            na.omit()
          wtsaux <- dat[,wts]
      }
      # No controls and no fes
      mods[[k]] <- felm(as.formula(
        paste(c(j,paste(i,paste('',0,0,cls, sep = '|'), sep = '')),
              collapse = '~')), data = dat, weights = wtsaux)
      moddescr <- rbind(moddescr, 
                        data.frame(outc = j, 
                                   treat = i,
                                   hCtrls = F,
                                   hFEs = F))
      print(k); k = k+1
      # Controls and no fes
      mods[[k]] <- felm(as.formula(
        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
                        paste('',0,0,cls, sep = '|'), sep = '')),
              collapse = '~')), data = dat, weights = wtsaux)
      moddescr <- rbind(moddescr, 
                        data.frame(outc = j, 
                                   treat = i,
                                   hCtrls = T,
                                   hFEs = F))
      print(k); k = k+1
      # No controls and fes
      mods[[k]] <- felm(
        as.formula(paste(c(j,paste(paste(c(i), collapse = '+'),
                                   paste('',fes_mod,0,cls, sep = '|'), 
                                   sep = '')),
                         collapse = '~')), data = dat, weights = wtsaux)
      moddescr <- rbind(moddescr, 
                        data.frame(outc = j, 
                                   treat = i,
                                   hCtrls = F,
                                   hFEs = T))
      print(k); k = k+1
      # Controls and fes
      mods[[k]] <- felm(as.formula(
        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
                        paste('',fes_mod,0,cls, sep = '|'), sep = '')),
              collapse = '~')), data = dat, weights = wtsaux)
      moddescr <- rbind(moddescr, 
                        data.frame(outc = j, 
                                   treat = i,
                                   hCtrls = T,
                                   hFEs = T))
      print(k); k = k+1
    }
  }
  return(list(moddescr, mods))
}

@@

resInt2 <- calcATEs(outcs, 'treat', ctrls, fes, cls, dat = impact_evaluation_phase2, wts = 'IPW_treat')

# Results intervention 2
library(stargazer)
stargazer(resInt2[[2]][[4]],resInt2[[2]][[8]],resInt2[[2]][[12]],
          resInt2[[2]][[16]],resInt2[[2]][[20]],resInt2[[2]][[24]],
          title = '\\label{tab:results2} Impact Evaluation -- Intervention 2',
          dep.var.labels.include=F, 
          keep='treatTreatment', type = 'latex',
          covariate.labels = 'ATE',
          column.labels = c("Investment & Investment & Delta & Finished & Cancelled & Updated \\\\ & Before & After & Investment & Construction & Construction & Date \\\\"),
          column.sep.width = '-2pt',
          omit.stat=c('adj.rsq', 'ser'), align=F, digits=2,
          notes = c('Cluster-robust SEs at the municipality level.', 'IPW computed by the randomizr package.'),
          add.lines = list(c("Controls", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
            c("State Fixed Effects", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes")),
          notes.append = T, header=FALSE)
```

@@

\begin{table}[!htbp] \centering 
  \caption{\label{tab:results2} Impact Evaluation -- Intervention 2} 
  \label{} 
\begin{tabular}{@{\extracolsep{-2pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
\cline{2-7} 
 & Investment & Investment & Delta & Finished & Cancelled & Updated \\ & Before & After & Investment & Construction & Construction & Date \\ &  &  &  &  &  \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
\hline \\[-1.8ex] 
 ATE & $-$1.33 & $-$2.26 & $-$0.94 & $-$0.001 & 0.01 & 0.002 \\ 
  & (1.45) & (1.56) & (0.61) & (0.01) & (0.01) & (0.02) \\ 
  & & & & & & \\ 
\hline \\[-1.8ex] 
Controls & Yes & Yes & Yes & Yes & Yes & Yes \\ 
State Fixed Effects & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 3,226 & 3,226 & 3,226 & 3,226 & 3,226 & 3,109 \\ 
R$^{2}$ & 0.12 & 0.11 & 0.04 & 0.02 & 0.17 & 0.09 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{6}{r}{Cluster-robust SEs at the municipality level.} \\ 
 & \multicolumn{6}{r}{IPW computed by the randomizr package.} \\ 
\end{tabular} 
\end{table}

@@

# Function for custom randomization inference
test_fun <- function(dat, outc, treat, wts = NULL) {
  ctrls_mod <- paste(ctrls, collapse = '+')
  fes_mod <- paste(fes, collapse = '+')
  moddescr <- data.frame()
  mods <- list()
  if(is.null(wts)) {
    dat <- dat %>%
      select(one_of(c(outc, treat, ctrls, fes, cls))) %>%
      na.omit()
    wtsaux <- NULL
  } else {
    dat <- dat %>%
      select(one_of(c(outc, treat, ctrls, fes, cls, wts))) %>%
      na.omit()
    wtsaux <- dat[,wts]
  }
  aux <- 
    felm(as.formula(
      paste(c(outc,paste(paste(c(treat,ctrls_mod), collapse = '+'),
                        paste('',fes_mod,0,cls, sep = '|'), sep = '')),
              collapse = '~')), data = dat, weights = wtsaux)
  return(aux$coefficients[1])
}

@@

# First experiment
set.seed(543129) #Random.org
auxdat <- impact_evaluation_phase1[,c('ibge_code7', outcs, ctrls, fes, cls)]
aux2 <- unique(impact_evaluation_phase1[,c('ibge_code7', 'treat')]) %>% na.omit()
N = sum(table(aux2$treat))
Ctrl = 150
resri1 <- data.frame(1:1000)
for (k in 1:1000) {
    treat <- c(rep(1,N-Ctrl), rep(0,Ctrl))
    treat <- sample(treat, N)
    aux2 <- data.frame(aux2, treat = treat)
}
auxdat <- left_join(auxdat, aux2)
for (i in outcs) {
  res <- numeric()
  for (k in 1:1000) 
    res[k] <- test_fun(auxdat, i, paste('treat', k, sep = '.'))
  resri1 <- data.frame(resri1, res)
  names(resri1)[names(resri1)=='res'] = i
}
resri1 <- resri1[,-1]
i1h1 <- ggplot(data=resri1, aes(resri1$percExecBegin)) + 
  geom_histogram(bins = 100) + 
  geom_vline(xintercept = test_fun(impact_evaluation_phase1, 'percExecBegin', 'treat'),
             lwd = 1, lty = 2) +
  labs(x="Percentage Completed Before\n(placebo)", y="Frequency")
i1h2 <- ggplot(data=resri1, aes(resri1$percExecEnd)) + 
  geom_histogram(bins = 100) + 
  geom_vline(xintercept = test_fun(impact_evaluation_phase1, 'percExecEnd', 'treat'),
             lwd = 1, lty = 2) +
  labs(x="Percentage Completed End Intervention", y="Frequency")
i1h3 <- ggplot(data=resri1, aes(resri1$deltaPercExec)) + 
  geom_histogram(bins = 100) + 
  geom_vline(xintercept = test_fun(impact_evaluation_phase1, 'deltaPercExec', 'treat'),
             lwd = 1, lty = 2) +
  labs(x="Diff. Pct. Completed Before and After", y="Frequency")
i1h4 <- ggplot(data=resri1, aes(resri1$isFinished)) + 
  geom_histogram(bins = 100) + 
  geom_vline(xintercept = test_fun(impact_evaluation_phase1, 'isFinished', 'treat'),
             lwd = 1, lty = 2) +
  labs(x="Finished School Construction Indicator", y="Frequency")
i1h5 <- ggplot(data=resri1, aes(resri1$isCancelled)) + 
  geom_histogram(bins = 100) + 
  geom_vline(xintercept = test_fun(impact_evaluation_phase1, 'isCancelled', 'treat'),
             lwd = 1, lty = 2) +
  labs(x="Cancelled School Construction Indicator", y="Frequency")
i1h6 <- ggplot(data=resri1, aes(resri1$updDate)) + 
  geom_histogram(bins = 100) + 
  geom_vline(xintercept = test_fun(impact_evaluation_phase1, 'updDate', 'treat'),
             lwd = 1, lty = 2) +
  labs(x="Updated Endline Date School Construction", y="Frequency")

@@

We also note that effect sizes are small in all estimations and coefficients flip signs in all but one of our six dependent variables. This provides further evidence for the null results: not only the app would have a low impact even if the treatment were significant, but the results could go against what the bottom-up accountability theory predicts. At least in the school construction outcomes we investigate here, we find little evidence that grassroots monitoring works. This inconsistent directions for the effects reassure us that the null is not only a matter of statistical power.
